The Right Way to Search Evolving Graphs

### 2016-02-01 paper.tex
HYPERLINKS NOT ALLOWED BY IEEE
Add arXiv build target
Also fix typo
Fix embarrassing typo

\usepackage{hyperref}
% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

@@

\begin{abstract}
Evolving graphs arise in many different contexts where the
interrelations between data elements change over time.
We present a breadth first search (BFS) algorithm for evolving graphs
that can track (active) nodes correctly.
Using simple examples, we show na\"ive matrix-matrix multiplication on
time-dependent adjacency matrices miscounts the number of temporal paths.
By mapping an evolving graph to an adjacency matrix of the equivalent static graph,
we prove the properties of the BFS algorithm using the properties of the
adjacency matrix. Finally, demonstrate how the BFS over evolving graphs can be
applied to mining citation networks.

@@

  \foreach \from/\to in {n10/n7, n1/n4, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $t_1$, $t_2$ and $t_3$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges are shown as black errors.}
\label{fig:eg_shortest_path}
\end{figure}

>>>>

% NOT ALLOWED BY IEEE
% \usepackage{hyperref}
% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

@@

\begin{abstract}
Evolving graphs arise in many different contexts where the
interrelations between data elements change over time.
We present a breadth first search (BFS) algorithm for evolving graphs
that can track (active) nodes correctly.
Using simple examples, we show that na\"ive matrix-matrix multiplication on
time-dependent adjacency matrices miscounts the number of temporal paths.
By mapping an evolving graph to an adjacency matrix of the equivalent static graph,
we prove the properties of the BFS algorithm using the properties of the
adjacency matrix. Finally, demonstrate how the BFS over evolving graphs can be
applied to mining citation networks.

@@

  \foreach \from/\to in {n10/n7, n1/n4, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $t_1$, $t_2$ and $t_3$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges are shown as black arrows.}
\label{fig:eg_shortest_path}
\end{figure}
